\documentclass{article}

\usepackage{booktabs}
\title{SE 3XA3: Development Plan\\Shuffle+}

\author{Team 16, ASK Studios
		\\ Aidan Schonewille, schonea
		\\ Sullivan Stobo, stobos
		\\ Karlo Delalic, delalik
}

\date{September 27, 2017}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabular}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 27, 2017 & Aidan\/Sullivan\/Karlo & Initial setup of document, starting Team Meeting, Communication, Roles \& Technology sections.\\
Date2 & Name(s) & Description of changes\\
... & ... & ...\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\maketitle

\newpage

Put your introductory blurb here.

\section{Team Meeting Plan}
The team will meet Tuesdays at 2:30 at Thode Library, as needed.  The scribe role will rotate between the team members, and they will also be responsible for holding the meeting.  At the meetings, the upcoming deadlines will be discussed, as well as any tasks currently being worked on not finished before the previous meeting.

\section{Team Communication Plan}
The team will learn and utilize Git issues for codebase issues, and will give a further reminder through instant messaging.  The team will primarily communicate through Allo, where all members are in a group chat.  The team members have downloaded this application on all of our phones, and will be used for topics such as planning the next meeting, making sure deliverables have been properly submitted and tagged on time and miscellaneous project questions.

\section{Team Member Roles}
\begin{tabular}{|c|c|}
\hline
Member&Expertise\\
\hline
Aidan Schonewille&-\\
Sullivan Stobo&-\\
Karlo Delilac&-\\
\hline
\end{tabular}
\section{Git Workflow Plan}

\section{Proof of Concept Demonstration Plan}

\section{Technology}
The project will be written in HTML5 and JavaScript, using CSS for visual design.  The code will be written in the team member's preferred text editor, such as Notepad++.  The project will be tested in various major web browsers on our personal work systems, such as Mozilla Firefox and Google Chrome.
\section{Coding Style}

\section{Project Schedule}

Provide a pointer to your Gantt Chart.

\section{Project Review}

\end{document}