\documentclass{article}

\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{color}

\title{SE 3XA3: Development Plan\\Shuffle}

\author{Team 16, ASK Studios
        \\ Aidan Schonewille, schonea
        \\ Sullivan Stobo, stobos
        \\ Karlo Delalic, delalik
}

\date{\today}

\begin{document}

\section*{Revision History}
\begin{center}
\begin{tabular}{| c | c | p{6cm} |}
\hline
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\hline
September 27, 2017 & Aidan/Sullivan/Karlo & Initial setup of document, starting Team Meeting, Communication, Roles \& Technology sections.\\
\hline
September 29, 2017 & Aidan/Sullivan/Karlo & Filled the remaining sections from last lab.\\
\hline
November 27, 2017 & Sullivan & Updated document to reflect feedback received \\
\hline
December 5, 2017 & Sullivan & Finalized \\
\hline
\end{tabular}
\end{center}

\newpage

\maketitle

\newpage

\section*{Intoduction}
Shuffle will generate a personalized playlist based on the user's input and preferences. It will act a alternative to the major music streaming services. Shuffle will provide a random play list of music videos based on a query provided by the user.  It will then play these music videos back to back without interruption.

\section{Team Meeting Plan}
The team will meet Tuesdays at 2:30 at Thode Library, as needed. The scribe role will rotate between the team members, and they will also be responsible for holding the meeting. At the meetings, the upcoming deadlines will be discussed, as well as any tasks currently being worked on that have not finished before the previous meeting.

\section{Team Communication Plan}
The team will learn and utilize Git issues for codebase issues and will give a further reminder through instant messaging. The team will primarily communicate through Discord, where all members are in a group chat. The team members have downloaded this application on all of our phones, and will be used for topics such as planning the next meeting, making sure deliverables have been properly submitted and tagged on time and miscellaneous project questions.  \color{red}Team members will be available at most hours using this method of communication making it ideal.\color{black}

\section{Team Member Roles}
\begin{tabular}{|c|c|}
\hline
Member&Expertise\\
\hline
Aidan Schonewille&Documentation\\
Sullivan Stobo&Frontend\\
Karlo Delalic&Project Leader\\
\hline
\end{tabular}
\section{Git Workflow Plan}

We will use the centralized git workflow plan, as there are only three of us. The centralized work flow utilizes only one branch, but due to the small size of the project there should \color{red}not \color{black}be many conflicts to resolve. Tags will be used to indicate a working version of a feature. We will set milestones for major features and complete then as they are implemented. \color{red}Issues will be used to document bugs that need to be fixed and they will be closed when the corresponding bug has been fixed. \color{black}Issues will also be used to indicate what still needs to be implemented for the project to be completed.


\newpage
\section{Proof of Concept Demonstration Plan}

We suspect the algorithm for finding suitable videos/songs will be one of the more difficult parts of the project. Major time will be given to this. Due to the random nature of our project, testing will be difficult. There are many genres to test and a huge number of videos. Libraries are not a concern. The music playing feature may be difficult to implement on mobile.
\\
\\
For our proof of concept demonstration we plan to have at least an implementation of YouTube’s related videos for playing new songs. We plan on having a basic webpage created as well.

\section{Technology}

The project will be written in HTML5 and JavaScript using React.js. The code will be written in the team member's preferred text editor, such as Notepad++. The project will be tested in various major web browsers on our personal work systems, such as Mozilla Firefox and Google Chrome. YouTube's infinity frame API and Data API will be used for the searching and playing of videos.

\section{Coding Style}

We will makes use of Google’s guidelines for JavaScript coding style.

\section{Project Schedule}

\href{https://gitlab.cas.mcmaster.ca/delalik/Shuffle/blob/master/ProjectSchedule/Shuffle.gan}{View our Gantt chart here.}

\section{Project Review}
\color{red}
We can easily say that this project was very much so a success.  We are very proud of the webpage we produce and deeply enjoyed the process of making it.  We got hands on experience with using React.js, which is excellent as it becoming more and more common in web development.  We also learned a whole lot about the software development life cycle.  This will most definitely be useful to all of us in future careers.  This was really a fantastic experience that we were all glad to have had a chance to do. 

\end{document}

